\bf Model Visualization Techniques for a Social Network Model

### 2017-04-13 paper.Rnw
split up animation figure by add, remove

# running Siena
friendship <- sienaDependent(friendshipData)
alcohol <- varCovar(drink[20:35,])
mydata <- sienaDataCreate(friendship, alcohol)
myeffnull <- getEffects(mydata)
myalgorithm <- sienaAlgorithmCreate(projname = 's16_3')
set.seed(823746)
load("data/ansnullpaper.rda")
ansnullchains <- get_chain_info(ansnull)
ansnullchains %>%
  filter(period == 1) %>%  #only look at chains from wave 1 to wave 2
  group_by(rep) %>%
  select(rep, from = ego, to = alter) %>%
  mutate(val = as.numeric(!from == to),
         from = paste0("V", parse_number(from)+1), # make the chains
         to = paste0("V", parse_number(to)+1)) -> ansnullchainsw1w2
colnames(fd2.w1) <- paste0("V", 1:16)
rownames(fd2.w1) <- paste0("V", 1:16)
wave1friends <- fortify(as.adjmat(fd2.w1))
ms1 <- listMicrosteps(dat = wave1friends,
                      microsteps = filter(ansnullchainsw1w2, rep == 1))
microsteps <- ms1[1:9]

microsteps_df <- getMicrostepsDF(microsteps)
pte <- pretween_edges(microsteps = microsteps)
ptv <- pretween_vertices(pte = pte, layoutparams = list(n = 16))

# get tweened data for all microsteps
pall <- tween_microsteps(ptv, pte, microsteps_df)

static_pall <- filter(pall, .frame %in% (1:12 * 3-2))

create_net_animate(static_pall) + 
  facet_wrap(~.frame, nrow=3, labeller = 'label_both') + 
  theme(panel.background = element_rect(color = 'black'))
@

XX INSERT DESCRIPTION OF THE MOVIE - WHAT IT ALLOWS US TO SEE, ETC. XX

>>>>

# running Siena
friendship <- sienaDependent(friendshipData)
alcohol <- varCovar(drink[20:35,])
mydata <- sienaDataCreate(friendship, alcohol)
myeffnull <- getEffects(mydata)
myalgorithm <- sienaAlgorithmCreate(projname = 's16_3')
set.seed(823746)
load("data/ansnullpaper.rda")
ansnullchains <- get_chain_info(ansnull)
ansnullchains %>%
  filter(period == 1) %>%  #only look at chains from wave 1 to wave 2
  group_by(rep) %>%
  select(rep, from = ego, to = alter) %>%
  mutate(val = as.numeric(!from == to),
         from = paste0("V", parse_number(from)+1), # make the chains
         to = paste0("V", parse_number(to)+1)) -> ansnullchainsw1w2
colnames(fd2.w1) <- paste0("V", 1:16)
rownames(fd2.w1) <- paste0("V", 1:16)
wave1friends <- fortify(as.adjmat(fd2.w1))
ms1 <- listMicrosteps(dat = wave1friends,
                      microsteps = filter(ansnullchainsw1w2, rep == 1))
microsteps <- ms1[1:20]

microsteps_df <- getMicrostepsDF(microsteps)
pte <- pretween_edges(microsteps = microsteps)
ptv <- pretween_vertices(pte = pte, layoutparams = list(n = 16))
# step 1 is remove, step 9 is add. 
# get tweened data for all microsteps
pall <- tween_microsteps(ptv, pte, microsteps_df)

static_pall <- filter(pall, .frame %in% c(15,20,22,24,26:28, 71:73, 75, 79, 81, 84))

static_pall$type <- NA
static_pall$type[which(static_pall$.frame %in% c(15,20,22,24,26:28))] <- "Remove Edge"
static_pall$type[which(static_pall$.frame %in% c(71:73, 75, 79, 81, 84))] <- "Add Edge"

set.seed(34569234)
create_net_animate(static_pall) + 
  facet_wrap(~.frame, nrow=2, labeller = 'label_both') + 
  theme(panel.background = element_rect(color = 'black'))
@

The top row of Figure~\ref{makinggif} shows an edge being removed, and the bottom row shows one being added. In both cases
